\begin{abstract}
We consider the problem of covering/connecting a multi-interface network with a minimum cost assignment of interfaces to vertices. In the \textsc{Coverage} problem we demand that every edge is covered by at least one common interface assigned to its endpoints. In the \textsc{Connectivity} problem we are additionally given a set of disjoint groups of terminals $U_1,\ldots,U_p \subseteq V$ and we demand that the subgraph of activated edges spans each group $U_i$. The cost of activating an interface at a vertex is given by a non-negative function $c\colon V\times [k]\to \mathbb{N}$, where $k$ is the number of interfaces. We wish to minimize the maximum cost of an activated interface.

For the \textsc{Coverage} problem we give the first $O\br{\log m}$-approximation algorithm based on a randomized rounding of a natural, set-cover-style linear programming relaxation. We also show how to use this LP to obtain a $k$-approximation algorithm, where $k$ is the number of interfaces. This improves the previously best known $O\br{\ln\Delta+b\cdot\min\brc{\ln \Delta,c_{\text{max}}}}$-approximation, where $b$ is a certain parameter of the input instance which can be as large as $\Omega\br{n}$ and $c_{\text{max}}$ is the maximum cost of activating an interface and $O\br{k}$-approximation for the uniform cost case [Algorithmica 2012]. 
% For min-sum covering this improves the previously best known $O\br{\sqrt{n}\cdot\log n}$-approximation and generalizes the $O\br{k}$-approximation [Wireless Networks 2009]. 
For the \textsc{Connectivity} problem we devise an $O\br{\log^2 m}$-approximation algorithm, which is the first non-trivial approximation algorithm for this problem. The algorithm is based on a similar LP relaxation with additional cut constraints to ensure connectivity of all terminal groups. The rounding procedure is similar to the one for the \textsc{Coverage} problem but requires a more careful analysis to ensure that the connectivity constraints are satisfied with high probability.
% We also give combinatorial algorithms with $O\br{\Delta}$ guarantees for both min-sum and min-max covering as well as min-sum connection thus improving on the previously known $O\br{\Delta\cdot c_{\text{max}}}$ for the min-max covering.

% We complement these results by showing that both the min-sum covering and connecting cannot be approximated within a factor of $\br{1-o\br{1}}\cdot \ln n$ even on stars, unless $P=NP$. We also show, by an approximation-preserving reduction to the min-sum covering assignment problem on bipartite graphs with unit costs, that min-sum covering cannot be approximated within a factor of $o\br{\log \Delta}$ unless $P=NP$.
\end{abstract}

