\section{Preliminaries}

Let $G=\br{V, E}$ be a connected simple graph. Let $[k]$ be the set of different types of interfaces across the network and let $\lambda\colon V \to 2^{[k]}$ be a function that assigns to each vertex $v\in V$ its set of available interfaces such that for each edge $uv \in E$, $\lambda\br{u} \cap \lambda\br{v} \neq \emptyset$.
An assignment of active interfaces is a function $\lambda_A\colon V \to 2^{[k]}$ such that $\lambda_A\br{v} \subseteq \lambda\br{v}$ for all $v\in V$. We say that an edge $uv \in E$ is \emph{covered} if $\lambda_A\br{u} \cap \lambda_A\br{v} \neq \emptyset$. We denote by $\cov\br{\lambda_A} = \{uv \in E : \lambda_A\br{u} \cap \lambda_A\br{v} \neq \emptyset\}$ the set of edges covered by $\lambda_A$, and by $G_A$ the subgraph of $G$ with edge set $\cov\br{\lambda_A}$.

In the \textsc{Coverage} problem, we wish to find an assignment of active interfaces $\lambda_A$ such that $G_A=G$. We call such an assignment a \emph{covering assignment}.

In the \textsc{Connectivity} problem, we are additionally given $p\geq 1$ pairwise disjoint groups of \emph{terminals} $U_1, U_2, \dots, U_p \subseteq V$ and we wish to find an assignment of active interfaces $\lambda_A$ such that for every $r\in[p]$, all vertices in $U_r$ lie in the same connected component of $G_A$. Vertices in $V\setminus\bigcup_{r=1}^{p}U_r$ may be used as Steiner vertices. We call such an assignment a \emph{connecting assignment}. The special case $p=1$ with $U_1=V$ corresponds to requiring that $G_A$ is a connected spanning subgraph of $G$.

We are also given a cost function $c\colon [k]\times V \to \mathbb{N}_{\geq 0}$, which denotes the cost of activating the interface $i\in[k]$ in the vertex $v\in V$. For an assignment $\lambda_A$, we define the \emph{cost at vertex} $v$ as:
$$\COST\br{v, \lambda_A} = \sum_{i\in\lambda_A\br{v}}c\br{i, v}.$$
Based on this, we consider two global cost criteria. The \emph{max cost} of an assignment $\lambda_A$ is:
$$\COST_M\br{\lambda_A}=\max_{v\in V} \COST\br{v, \lambda_A}$$
and the \emph{sum cost} of an assignment $\lambda_A$ is:
$$\COST_S\br{\lambda_A}=\sum_{v\in V} \COST\br{v, \lambda_A}.$$
The goal of the min-max (resp. min-sum) assignment problem is to find an assignment $\lambda_A$ that minimizes $\COST_M$ (resp. $\COST_S$).
The considered problems are formalized below:

\pbdef{\textsc{Coverage Problem}}{A connected simple graph $G=(V,E)$, available interfaces $\lambda\colon V \to 2^{[k]}$, a cost function $c\colon [k]\times V \to \mathbb{N}_{\geq 0}$.}{Find a min-max (resp. min-sum) covering assignment $\lambda_A$ minimizing $\COST_M\br{\lambda_A}$ (resp. $\COST_S\br{\lambda_A}$).}

\pbdef{\textsc{Connectivity Problem}}{A connected simple graph $G=(V,E)$, available interfaces $\lambda\colon V \to 2^{[k]}$, a cost function $c\colon [k]\times V \to \mathbb{N}_{\geq 0}$, pairwise disjoint groups of terminals $U_1,\dots,U_p \subseteq V$.}{Find a min-max (resp. min-sum) connecting assignment $\lambda_A$ minimizing $\COST_M\br{\lambda_A}$ (resp. $\COST_S\br{\lambda_A}$).}

Throughout this paper, unless stated otherwise, we focus on the \emph{min-max} cost criterion. Therefore, we will simply write $\COST\br{\lambda_A}$ instead of $\COST_M\br{\lambda_A}$ and we will refer to the min-max assignment problem as the \textsc{Coverage} and \textsc{Connectivity} problems, respectively. We will explicitly state when we consider the min-sum cost criterion.

\subsection{Probabilistic tools}

Additionally, we will need the following probability facts:
\begin{theorem}[Markov's Inequality]
Let $X$ be a non-negative random variable and $a > 0$. Then:
\[
    \Pr[X \geq a] \leq \frac{\mathbb{E}[X]}{a}.
\]
\end{theorem}

\begin{theorem}[\cite{OnCumulativeSumsOfRandomVariables} Wald's Identity]
Let $X_1, X_2, \dots$ be i.i.d.\ random variables with finite expectation $\mathbb{E}[X]$, and let $N$ be a non-negative integer-valued random variable independent of the sequence $(X_i)_{i\geq 1}$ with finite expectation $\mathbb{E}[N]$. Then:
\[
    \mathbb{E}\!\left[\sum_{i=1}^{N} X_i\right] = \mathbb{E}[N]\cdot\mathbb{E}[X].
\]
\end{theorem}

\begin{theorem}[(weighted) Chernoff Bound]
    Let $X_1, X_2, \dots, X_n$ be independent random variables taking values in $[0,1]$, let $w_1, w_2, \dots, w_n$ be non-negative weights, such that for every $i\in [n]$ we have that $w_i\in [0,1]$. Let $X=\sum_{i=1}^{n} w_i\cdot X_i$ and let $\mu = \E{X}$. Then for every $\delta_1 > 0$ and $\delta_2 \in (0,1)$ we have that:
    \[
        \Pr\br{X \geq (1+\delta_1)\cdot \mu} \leq \br{\frac{e^{\delta_1}}{(1+\delta_1)^{1+\delta_1}}}^\mu
        \qquad
        \Pr\br{X \leq (1-\delta_2)\cdot \mu} \leq \br{\frac{e^{-\delta_2}}{(1-\delta_2)^{1-\delta_2}}}^\mu.
    \]
\end{theorem}

The proof of the above fact follows the proof of the standard Chernoff bound and we include it in the appendix for completeness.

\subsection{Preprocessing for \textsc{min-max} problems}

Due to technical reasons, we show how to produce a polynomial number of instances, with cost function bounded by a polynomial in $n$. By testing consecutive powers of $2$, we find the smallest number $b$, such that the costliest activated interface in the optimal solution has cost at most $2^b$. For each vertex $v\in V$, we discard all of the interfaces from $\lambda\br{v}$ with cost larger than $2^b$ and we normalize the costs of remaining interfaces by dividing them by $2^b$. Note that the number of guesses is polynomial. We also can assume that $\OPT\geq 1/2$, since the cost of any solution is at least the cost of activating one interface, which is at least $1/2$ by our rounding.